---
title: "W201 Portfolio"
author: "Matthew Prout"
date: "MIDS Fall 2017"
site: bookdown::bookdown_site
documentclass: book
---

<!-- This won't be displayed but it will initialize your R session. Add any R libraries you need here. -->
```{r init,include=FALSE,echo=FALSE}
library(magrittr)
```

# Welcome! {-}

<!-- Below this line is just examples of how you can embed video from Google Drive. First you have to enable sharing, then just get the object ID which is that long string between d/ and /preview and will also be appended to any sharing link you generate for your video. -->
<p>
```{r echo=FALSE,fig.cap='Stump Speech',fig.align='center'}
knitr::include_url('https://drive.google.com/a/berkeley.edu/file/d/1h_KxU-k23ETdsrqyyQEqw_UalSgDwH-D/preview')
```

### Abstract: Senior Sentry Service

Many Americans who are retiring opt to live in independent living facilities.  Serious issues can arise if they start to have health issues and no one is there to take notice.

The solution is the Senior Sentry Service that monitors the senior using a fitness tracker.  Information about the senior’s vital signs, sleep patterns, and movement can be monitored, and machine learning would be used to detect abnormal conditions based on the data and the user’s profile.  The system generates an alert that is sent to a health service with information about the event.  A nurse could then make a house call to the senior if necessary, and also contact the senior's family.

This solution will save seniors money by allowing them to live in independent living facilities rather than in more expensive assisted living facilities.  The system will give family members piece of mind knowing that their parents are being monitored, and will reduce healthcare costs through the early detection of medical conditions.

### Abstract: Animal Shelter Outcome Improvement

Over a million animals each year are euthanized because shelters cannot find enough people to adopt the animals they have.  Animal shelters have the desire to see that their often limited resources are spent in a way that brings the most favorable outcomes to as many animals as possible.

The solution is a service that predicts the outcome of animals based on characteristics of the animal.  The service would employ a classification model that would provide recommendations on how the improve the animal of each animal, along with a probability of their outcome after the recommendation has been implemented.  This information could then guide shelters on how to direct their resources to particular animals.  A secondary feature of the service would be a web portal for people to search for pets to adopt.  This could be extended in the future to enable matching of animals with people who want to adopt.

As a result of the solution, the outcome of more animals will be improved by finding homes for them, and the number of animals that are euthanized will be reduced.

## About the author {-}

TODO

*Updated: `r Sys.Date()`*
